Details of specific functions

### 2020-07-14 inst/gitbook/03_specific-tutorials.Rmd
updated gitbook

### Time-slicing

@@

#### `test.metric`

@@

### NPMANOVA in `dispRity`

@@

### `geiger::dtt` model fitting in `dispRity`

@@

### null morphospace testing with `null.test`

@@

## Fitting modes of evolution to disparity data

@@

## Disparity as a distribution

@@

## Disparity from other matrices

>>>>

### Time-slicing {#time-slicing}

@@

#### `test.metric` {#test-metric}

@@

### NPMANOVA in `dispRity` {#adonis}

@@

### `geiger::dtt` model fitting in `dispRity` {#dtt}

@@

### null morphospace testing with `null.test` {#null-test}

@@

## Fitting modes of evolution to disparity data {#model-fitting}

@@

## Disparity as a distribution {#disparity-distribution}

@@

## Disparity from other matrices {#other-matrices}
